Precise, Second-Order Verification

### 2014-11-13 slides/nus-talk.tex
NUS talk slides

@@

%\author{Cristina David \and Daniel Kroening \and Matt Lewis}
\title{Everything You Ever Wanted To Prove About Termination But Were Afraid To Try}
%\subtitle{}
%\institute{Oxford University}
\date{\today}

@@

\begin{frame}{Outline}
  \tableofcontents
\end{frame}

@@

>>>>

\newcommand{\hpathlen}{\ensuremath{\mathit{pathLength}}\xspace}
\newcommand{\halloc}{\ensuremath{\mathit{new}}\xspace}
\newcommand{\hassign}{\ensuremath{\mathit{assign}}\xspace}
\newcommand{\hlookup}{\ensuremath{\mathit{lookup}}\xspace}
\newcommand{\hupdate}{\ensuremath{\mathit{update}}\xspace}
\newcommand{\halias}{\ensuremath{\mathit{alias}}\xspace}
\newcommand{\hisnull}{\ensuremath{\mathit{isNull}}\xspace}
\newcommand{\hispath}{\ensuremath{\mathit{isPath}}\xspace}
\newcommand{\hcircular}{\ensuremath{\mathit{circular}}\xspace}
%\newcommand{\id}{\ensuremath{\mathrm{id}}\xspace}
\newcommand{\hsubdivide}{\ensuremath{\mathit{subdivide}}\xspace}
\newcommand{\hfresh}{\ensuremath{\mathit{fresh}()}\xspace}

\newcommand{\defeq}{\ensuremath{\stackrel{\mathrm{def}}{=}}}

\newcommand{\kalashnikov}{{\sc Kalashnikov}\xspace}
\newcommand{\shakira}{{\sc Shakira}\xspace}

@@

\author{Cristina David \and Daniel Kroening \and Matt Lewis}
\title{Precise, Second-Order Verification}
%\subtitle{}
\institute{Oxford University}
\date{\today}

@@

\iffalse
\begin{frame}{Outline}
  \tableofcontents
\end{frame}
\fi

@@

\begin{frame}[fragile]{Heap}
 \centering
\begin{tikzpicture}
  %\node at (-.75,.25) {$h:$};

  \node (n1) {$\bullet$};
  \node (n2) [below of=n1] {$\bullet$};
  \node (n3) [right of=n1] {$\bullet$};
  \node (n4) [right of=n3] {$\bullet$};
  \node (n5) [right of=n4,above of=n4] {$\bullet$};
  \node (n6) [below of=n4] {$\bullet$};
  \node (x) [left of=n2] {$x$};
  \node (y) [right of=n5] {$y$};
  \node (z) [left  of=n1] {$z$};
  \node (null) [right=2em of n6] {\bf null};

  \path[draw,->] (n1) edge (n3)
		 (n2) edge (n3)
		 (n3) edge (n4)
		 (n4) edge[bend right=45] (n5)
		 (n5) edge[bend right=45] (n4);

  \path[dashed,->] (x) edge (n2)%
		   (y) edge (n5)%
		   (z) edge (n1)%
		   (null) edge (n6);
 \end{tikzpicture}
\end{frame}

\begin{frame}[fragile]{Heap Transformers}
 \centering
 \begin{tikzpicture}
  \node (n1) {$\bullet$};
  \node [right of=n1] (n2) {$\bullet$};
  \node (n3) [right of=n2] {$\bullet$};

  \node (y) [below=1em of n1] {$y$};
  \node (x) [right of=y] {$x$};
  \node (null) [right of=x] {\bf null};

  \path[draw, ->] (n1) edge (n2) (n2) edge (n3);
  \path[dashed,->] (x) edge (n3) (y) edge (n1) (null) edge (n3);

  \node (mid) [below right = .5em and 1em of n3] {$\Rightarrow$};

  \node [above right = .5em and 1em of mid] (m1) {$\bullet$};
  \node (m2) [right of = m1] {$\bullet$};
  \node (m3) [right of = m2] {$\bullet$};

  \node (y) [below=1em of m1] {$y$};
  \node (x) [right of=y] {$x$};
  \node (null) [right of=x] {\bf null};

  \path[draw, ->] (m1) edge (m2) (m2) edge (m3);
  \path[dashed,->] (x) edge (m2) (y) edge (m1) (null) edge (m3);
 \end{tikzpicture}
 }

 \vfill
 $\hlookup(h, x, y)$ \\
 $x = y{\rightarrow}next;$
\end{frame}
